---
title: "ASLPrep figures"
date: "4/18/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(mgcv)
library(visreg)
library(reshape2)
library(ggpubr)
library(ggpattern)
library(plyr)
library(ggsignif)
library(lmerTest)
library(dplyr)
library(broom.mixed)
library(sjPlot)
library(sjmisc)
library(sjlabelled)
library(lme4)
```

# Creating the figures for the ASLPrep paper

Here we create all the figures with data plotted. The data reflect an
expanded sample included after the initial revision.


```{r load_data}

all_data <- read.csv('CBFData.csv')
names(all_data)
table(all_data$Datasets, all_data$CBFTYPE)

all_data = na.omit(all_data)
all_data = subset(all_data, 
  (CBF.GM < 120) & 
  (CBF.GM > 5) & 
  (CBF.GM / CBF.WM > 1) & 
  (FD < 1))
all_data = all_data[!duplicated(all_data),]
table(all_data$Datasets, all_data$CBFTYPE)


# Final demographics
scbf_only <- subset(all_data, CBFTYPE=="SCBF")
table(scbf_only$Datasets)
table(scbf_only$Datasets, scbf_only$sex, useNA="ifany")

ddply(scbf_only, .(Datasets), summarise,
      mean_age=mean(AGE), sd_age=sd(AGE), 
      min_age=min(AGE), max_age=max(AGE) )

nrow(scbf_only)
rm(scbf_only)
```


## Figure 2
Fig. 2 | ASLPrep quantifies CBF across sequences, scanners and the lifespan. 
a, CBF in GM and WM for each dataset. Boxes in each violin plot indicate
interquartile range with the median shown as a white dot. b, GM CBF across the
lifespan. The thick black line represents the predicted values from a
generalized additive model; the dashed lines indicate the 95% confidence 
interval (R2 = 0.50; P = 1.1 × 10−16)

```{r figure2}
datagm = all_data
datagm$CBF.WM =NULL
datagm$TP ='GM'
datagm$CBF=datagm$CBF.GM 
datagm$CBF.GM = NULL 

datawm = all_data
datawm$CBF.GM =NULL
datawm$TP ='WM'
datawm$CBF=datawm$CBF.WM  
datawm$CBF.WM = NULL 

datasets = rbind(datagm,datawm)

datasetsy = datasets[datasets$CBFTYPE =='SCBF',]
datasetsy = na.omit(datasetsy)
dodge <- position_dodge(width = 0.5)
dp <- ggplot(datasetsy, aes(x=Datasets,y=CBF,fill=TP),plot = FALSE) + 
  geom_violin(position = dodge,width = 1.4)+
  geom_boxplot(width=.1, outlier.colour=NA, position = dodge) 
dp=dp + theme_classic() + scale_x_discrete(limits = rev) + 
  labs(x = "Datasets", y = "CBF(mL/100g/min)") +
  theme(axis.title.x = element_text(size = rel(1.2))) +
  theme(axis.title.y = element_text(size = rel(1.2) ,vjust=-0.6)) + ylim(0,140) +
  theme(axis.text = element_text(size = rel(1.4))) + theme(axis.line = element_line(colour = 'black', size = 0.5)) +
  scale_fill_manual(values=c("#d95f0e","#756bb1")) + theme(legend.title = element_blank())

datay = all_data[all_data$CBFTYPE =='SCBF',]
pnc = datay[datay$Datasets=='PNC',]
nki = datay[datay$Datasets=='NKI',]
age = datay[datay$Datasets=='AGE',]
irr = datay[datay$Datasets=='IRR',]
ftd = datay[datay$Datasets=='FTD',]

#############################################################
cbf_Age_gam <- gam(CBF.GM ~ s(AGE, k=4) + sex + FD, method="REML", data = datay)

#####################
## Look at results ##
#####################
summary(cbf_Age_gam)

## Nonlinear age effect
Age_pval <- summary(cbf_Age_gam)$s.table[1,4]
Age_pval

####################################
## Visualize Nonlinear Age Effect ##
####################################
plotdata <- visreg(cbf_Age_gam,'AGE',type = "conditional",scale = "linear", plot = FALSE)
smooths <- data.frame(Variable = plotdata$meta$x, 
                      x=plotdata$fit[[plotdata$meta$x]], 
                      smooth=plotdata$fit$visregFit, 
                      lower=plotdata$fit$visregLwr, 
                      upper=plotdata$fit$visregUpr)
predicts <- data.frame(Variable = "dim1", 
                       x=plotdata$res$AGE,
                       y=plotdata$res$visregRes)

CBF_Age_plot <- ggplot() + xlim(8, 85)+ ylim(0,140) +
  #theme(legend.position = "none")  +
  labs(x = "Age (years)", y = "CBF(mL/100g/min)",) +
  theme(axis.title.x = element_text(size = rel(1.2))) + 
  theme(axis.title.y = element_blank(),axis.ticks.y = element_blank(),axis.text.y = element_blank()) +
  theme(axis.text = element_text(size = rel(1.2))) + theme(axis.line = element_line(colour = 'black', size = 0.5), axis.ticks.length = unit(.25, "cm")) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank()) +
  geom_point(data = predicts, aes(x, y), colour = "darksalmon", alpha=0.7 ) +  
  #geom_point(data=datay,aes(x=AGE, y=CBF.GM),size=1)+ 
  geom_point(data=pnc,aes(x=AGE, y=CBF.GM),shape=21,size=2,fill='#e34a33', color="white")+ 
  geom_point(data=nki,aes(x=AGE, y=CBF.GM),shape=21,size=2,fill="#3182bd", color="white")+ 
  geom_point(data=irr,aes(x=AGE, y=CBF.GM),shape=21,size=2,fill="#31a354", color="white")+ 
  geom_point(data=ftd,aes(x=AGE, y=CBF.GM),shape=21,size=2,fill="#d95f02", color="white")+ 
  geom_point(data=age,aes(x=AGE, y=CBF.GM),shape=21,size=2,fill="#c51b8a", color="white")+ 
  geom_line(data = smooths, aes(x = x, y = smooth), colour = "midnightblue",size=1) +
  geom_line(data = smooths, aes(x = x, y=lower), linetype="dashed", colour = "midnightblue", alpha = 0.9, size = 0.9) + 
  geom_line(data = smooths, aes(x = x, y=upper), linetype="dashed",colour = "midnightblue", alpha = 0.9, size = 0.9) +
  coord_cartesian(xlim = c(10.5,85), ylim = c(0,140))
  
dir.create("Figure2")
figure <- ggarrange(dp,CBF_Age_plot,
                    ncol = 2, nrow = 1,widths=c(1.5,1) )
ggsave("Figure2/Figure2.pdf", width=7, units="in", height=3,dpi=800)
write.csv(all_data, "Figure2/Figure2Data.csv")
figure

```

## Extended Data Figure 5

Extended Data Fig. 5 | Bayesian methods mitigate impact of in-scanner motion on CBF image quality.
The impact of motion on quality differed significantly among quantification approaches (linear mixed effects
 model, F = 529.13, p = 1.0 × 10−25). The envelope indicates the 95% confidence interval.
```{r extdatafigure5}
datay <- subset(all_data, Datasets != 'FTD')
scbf = datay[datay$CBFTYPE=='SCBF',]
scrub = datay[datay$CBFTYPE=='SCRUB',]
basil = datay[datay$CBFTYPE=='BASIL',]
pvc = datay[datay$CBFTYPE=='PVC',]

cols = c("LINE1"="#e34a33","LINE2"="#3182bd","LINE3"="#d95f02",'LINE4'="#c51b8a")

CBF_Age_plot <- ggplot() + xlim(0, 1.1)+ ylim(0,1.1) +
  #theme(legend.position = "none")  +
  
  theme(axis.title.x = element_text(size = rel(1.2))) +
  theme(axis.title.y = element_text(size = rel(1.2),vjust=-0.9)) + 
  theme(axis.text = element_text(size = rel(1.2))) + theme(axis.line = element_line(colour = 'black', size = 0.5), axis.ticks.length = unit(.25, "cm")) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank()) +
  #geom_point(data = predicts, aes(x, y), colour = "darksalmon", alpha=0.7 ) +  
  geom_point(data=scbf,aes(x=FD, y=QEI),size=1,color="red",alpha = 2/10)+ 
  geom_point(data=scrub,aes(x=FD, y=QEI),size=1,color="blue",alpha = 2/10)+ 
  geom_point(data=basil,aes(x=FD, y=QEI),size=1,color='darkgreen',alpha = 2/10)+ 
  #geom_point(data=pvc,aes(x=FD, y=QEI),size=1,color="#c51b8a")+ 

  geom_smooth(method='lm',data=scbf, aes(x=FD, y=QEI), color="red")+
  geom_smooth(method='lm',data=scrub,aes(x=FD, y=QEI), color="blue")+
  geom_smooth(method='lm',data=basil,aes(x=FD, y=QEI), color='darkgreen')+
  #geom_smooth(method='lm',data=pvc,aes(x=FD, y=QEI), color="#c51b8a") +
  labs(x = "FD (mm)", y = "QEI",color=cols)+ 
  scale_colour_manual(values=cols) + 
  scale_linetype_manual(values=cols) +
  scale_x_continuous(expand = c(0, 0)) + scale_y_continuous(expand = c(0, 0))
CBF_Age_plot

dir.create("ExtendedDataFigure5")
ggsave("ExtendedDataFigure5/ExtendedDataFigure5.pdf", width=5, units="in", height=4,dpi=800)
write.csv(datay, "ExtendedDataFigure5/ExtendedDataFigure5.csv")

# # do the statistics
pnc.model <- lmerTest::lmer(QEI ~ FD*CBFTYPE + AGE + sex + FD + (1 | sub ), data=datay)

cat("\nModel summary:\n")
summary(pnc.model)

cat("\n\nGet the overall interaction signficance using anova: \n")
anova(pnc.model)

sjPlot::plot_model(pnc.model, colors = "Set1",type = "int",show.data = TRUE) + theme(axis.title.x = element_text(size = rel(1.6))) +
            theme(axis.title.y = element_text(size = rel(1.6))) +
            theme(axis.text = element_text(size = rel(1.4))) + theme(axis.line = element_line(colour = 'black', size = 1.5), axis.ticks.length = unit(.25, "cm")) +
           theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank())  + scale_x_continuous(expand = c(0, 0)) +
           scale_y_continuous(expand = c(0, 0))
```

## Extended data figure 6

Extended Data Fig. 6 | CBF of gray and white matter across datasets. The 
distribution of cerebral blood flow (CBF) within grey matter (GM) and white
matter (WM) is displayed for each dataset, for each quantification option: 
the standard CBF model, BASIL (a), BASIL with partial volume correction (PVC;
b), and SCRUB (c). SCRUB could not be applied for the FTD dataset as an ASL 
timeseries is required; the sequence used for that study provided only a
single ∆M image. Boxes within each violin plot indicate interquartile range
with the median shown as a white dot.

```{r extdatafigure6}
# CBF GM
datagm = all_data
datagm$CBF.WM =NULL
datagm$TP ='GM'
datagm$CBF=datagm$CBF.GM 
datagm$CBF.GM = NULL 

#CBF WM 
datawm = all_data
datawm$CBF.GM =NULL
datawm$TP ='WM'
datawm$CBF=datawm$CBF.WM  
datawm$CBF.WM = NULL 

datasets = rbind(datagm,datawm)
dir.create("ExtendedDataFigure6")
write.csv(datasets, "ExtendedDataFigure6/ExtendedDataFigure6.csv")

# BASIL
datasetsy = datasets[datasets$CBFTYPE =='BASIL',]
datasetsy = na.omit(datasetsy)
dodge <- position_dodge(width = 0.5)
basil <- ggplot(datasetsy, aes(x=Datasets,y=CBF,fill=TP),plot = FALSE) + 
  geom_violin(position = dodge,width = 1.4)+
  geom_boxplot(width=.1, outlier.colour=NA, position = dodge) 
basil=basil + theme_classic() + scale_x_discrete(limits = rev) + 
  labs(x = "Datasets", y = "CBF(mL/100g/min)") +
  theme(axis.title.x = element_text(size = rel(1.6))) +
  theme(axis.title.y = element_text(size = rel(1.6),vjust=-0.2)) + ylim(0,140) +
  theme(axis.text = element_text(size = rel(1.4))) + theme(axis.line = element_line(colour = 'black', size = .5)) +
  scale_fill_manual(values=c("#d95f0e","#756bb1")) + theme(legend.position = "none")

# BASIL + PVC
datasetsy = datasets[datasets$CBFTYPE =='PVC',]
datasetsy = na.omit(datasetsy)

dodge <- position_dodge(width = 0.5)
pvc<- ggplot(datasetsy, aes(x=Datasets,y=CBF,fill=TP),plot = FALSE) + 
  geom_violin(position = dodge,width = 1.4)+
  geom_boxplot(width=.1, outlier.colour=NA, position = dodge) 
pvc=pvc + theme_classic() + scale_x_discrete(limits = rev) + 
  labs(x = "Datasets", y = "CBF(mL/100 g/min)") +
  theme(axis.title.x = element_text(size = rel(1.6))) +
  theme(axis.title.y = element_text(size = rel(1.6))) + ylim(0,140) +scale_fill_manual(values=c("#d95f0e","#756bb1"))+
  theme(axis.text = element_text(size = rel(1.4))) + theme(axis.line = element_line(colour = 'black', size = .5)) +
  theme(axis.title.y = element_blank(),axis.ticks.y = element_blank(),axis.text.y = element_blank()) +
theme(legend.position = "none")

# SCRUB
datasetsy = datasets[datasets$CBFTYPE =='SCRUB',]
datasetsy = na.omit(datasetsy)

dodge <- position_dodge(width = 0.5)
scrub <- ggplot(datasetsy, aes(x=Datasets,y=CBF,fill=TP),plot = FALSE) + 
  geom_violin(position = dodge,width = 1.4)+
  geom_boxplot(width=.1, outlier.colour=NA, position = dodge) 
scrub=scrub + theme_classic() + scale_x_discrete(limits = rev) + 
  labs(x = "Datasets", y = "CBF(mL/100 g/min)") +
  theme(axis.title.x = element_text(size = rel(1.6))) + scale_fill_manual(values=c("#d95f0e","#756bb1"))+
  theme(axis.title.y = element_text(size = rel(1.6))) + ylim(0,140) +
  theme(axis.text = element_text(size = rel(1.4))) + theme(axis.line = element_line(colour = 'black', size = .5)) +
theme(axis.title.y = element_blank(),axis.ticks.y = element_blank(),axis.text.y = element_blank()) +
theme(legend.position = "none")

# combine the 3
figure <- ggarrange(basil,pvc,scrub,
                    ncol = 3, nrow = 1,widths=c(2.5,2,1.5) )
ggsave("ExtendedDataFigure6/ExtendedDataFigure6.pdf", width=10, units="in", height=3,dpi=800)
figure
```

## Extended data figure 7
Extended Data Fig. 7 | CBF declines nonlinearly with age over the lifespan. 
Evolution of gray matter CBF with age over the lifespan across all five datasets.
For each dataset, we used four methods for quantifying CBF: the standard CBF 
model (see main text), BASIL (a), BASIL with partial volume correction
(PVC; b), and SCRUB (c). We used a generalized additive model with penalized 
splines to characterize the nonlinear evolution of CBF over age. The thick
black line represents the predicted values, while the dashed lines represent 
the 95% confidence intervals.

```{r extdatafigure7}
kk = 4 # order
dir.create("ExtendedDataFigure7")
write.csv(all_data, "ExtendedDataFigure7/ExtendedDataFigure7.csv")

# BASIL PLOT
datay = all_data[all_data$CBFTYPE =='BASIL',]
pnc = datay[datay$Datasets=='PNC',]
nki = datay[datay$Datasets=='NKI',]
age = datay[datay$Datasets=='AGE',]
irr = datay[datay$Datasets=='IRR',]
ftd = datay[datay$Datasets=='FTD',]

#############################################################
basil_Age_gam <- gam(CBF.GM ~ AGE + sex + FD + s(AGE, k=kk), method="REML", data = datay)

#####################
## Look at results ##
#####################
#summary(cbf_Age_gam)

## Nonlinear age effect
Age_pval <- summary(basil_Age_gam)$s.table[1,4]
Age_pval

####################################
## Visualize Nonlinear Age Effect ##
####################################
plotdata <- visreg(basil_Age_gam,'AGE',type = "conditional",scale = "linear", plot = FALSE)
smooths <- data.frame(Variable = plotdata$meta$x, 
                      x=plotdata$fit[[plotdata$meta$x]], 
                      smooth=plotdata$fit$visregFit, 
                      lower=plotdata$fit$visregLwr, 
                      upper=plotdata$fit$visregUpr)
predicts <- data.frame(Variable = "dim1", 
                       x=plotdata$res$AGE,
                       y=plotdata$res$visregRes)

basil_Age_plot <- ggplot() + xlim(8, 85)+ ylim(0,140) +
  #theme(legend.position = "none")  +
  labs(x = "Age (years)", y = "CBF(mL/100g/min)") +
  theme(axis.title.x = element_text(size = rel(1.6))) +
  theme(axis.title.y = element_text(size = rel(1.6),vjust=-1.2)) + 
  theme(axis.text = element_text(size = rel(1.4))) + theme(axis.line = element_line(colour = 'black', size = .5), axis.ticks.length = unit(.25, "cm")) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank()) +
  geom_point(data = predicts, aes(x, y), colour = "darksalmon", alpha=0.7 ) +  
  #geom_point(data=datay,aes(x=AGE, y=CBF.GM),size=1)+ 
  geom_point(data=pnc,aes(x=AGE, y=CBF.GM),shape=21,size=2,fill='#e34a33', color="white")+ 
  geom_point(data=nki,aes(x=AGE, y=CBF.GM),shape=21,size=2,fill="#3182bd", color="white")+ 
  geom_point(data=irr,aes(x=AGE, y=CBF.GM),shape=21,size=2,fill="#31a354", color="white")+ 
  geom_point(data=ftd,aes(x=AGE, y=CBF.GM),shape=21,size=2,fill="#d95f02", color="white")+ 
  geom_point(data=age,aes(x=AGE, y=CBF.GM),shape=21,size=2,fill="#c51b8a", color="white")+ 
  geom_line(data = smooths, aes(x = x, y = smooth), colour = "midnightblue",size=1) +
  geom_line(data = smooths, aes(x = x, y=lower), linetype="dashed", colour = "midnightblue", alpha = 0.9, size = 0.9) + 
  geom_line(data = smooths, aes(x = x, y=upper), linetype="dashed",colour = "midnightblue", alpha = 0.9, size = 0.9) +
  coord_cartesian(xlim = c(10.5,85), ylim = c(0,140))

# BASIL
datay = all_data[all_data$CBFTYPE =='PVC',]
pnc = datay[datay$Datasets=='PNC',]
nki = datay[datay$Datasets=='NKI',]
age = datay[datay$Datasets=='AGE',]
irr = datay[datay$Datasets=='IRR',]
ftd = datay[datay$Datasets=='FTD',]

#############################################################
pvc_Age_gam <- gam(CBF.GM ~ AGE + sex + FD + s(AGE, k=kk), method="REML", data = datay)

#####################
## Look at results ##
#####################
#summary(cbf_Age_gam)

## Nonlinear age effect
Age_pval <- summary(pvc_Age_gam)$s.table[1,4]
Age_pval

####################################
## Visualize Nonlinear Age Effect ##
####################################
plotdata <- visreg(pvc_Age_gam,'AGE',type = "conditional",scale = "linear", plot = FALSE)
smooths <- data.frame(Variable = plotdata$meta$x, 
                      x=plotdata$fit[[plotdata$meta$x]], 
                      smooth=plotdata$fit$visregFit, 
                      lower=plotdata$fit$visregLwr, 
                      upper=plotdata$fit$visregUpr)
predicts <- data.frame(Variable = "dim1", 
                       x=plotdata$res$AGE,
                       y=plotdata$res$visregRes)

pvc_Age_plot <- ggplot() + xlim(8, 85)+ ylim(0,140) +
  #theme(legend.position = "none")  +
  labs(x = "Age (years)", y = "CBF(mL/100 g/min)") +
  theme(axis.title.x = element_text(size = rel(1.6))) +
  theme(axis.title.y = element_text(size = rel(1.6))) + 
  theme(axis.text = element_text(size = rel(1.4))) + theme(axis.line = element_line(colour = 'black', size = .5), axis.ticks.length = unit(.25, "cm")) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank()) +
  geom_point(data = predicts, aes(x, y), colour = "darksalmon", alpha=0.7 ) +  
  #geom_point(data=datay,aes(x=AGE, y=CBF.GM),size=1)+ 
  geom_point(data=pnc,aes(x=AGE, y=CBF.GM),shape=21,size=2,fill='#e34a33', color="white")+ 
  geom_point(data=nki,aes(x=AGE, y=CBF.GM),shape=21,size=2,fill="#3182bd", color="white")+ 
  geom_point(data=irr,aes(x=AGE, y=CBF.GM),shape=21,size=2,fill="#31a354", color="white")+ 
  geom_point(data=ftd,aes(x=AGE, y=CBF.GM),shape=21,size=2,fill="#d95f02", color="white")+ 
  geom_point(data=age,aes(x=AGE, y=CBF.GM),shape=21,size=2,fill="#c51b8a", color="white")+ 
  geom_line(data = smooths, aes(x = x, y = smooth), colour = "midnightblue",size=1) +
  geom_line(data = smooths, aes(x = x, y=lower), linetype="dashed", colour = "midnightblue", alpha = 0.9, size = 0.9) + 
  geom_line(data = smooths, aes(x = x, y=upper), linetype="dashed",colour = "midnightblue", alpha = 0.9, size = 0.9) +
  coord_cartesian(xlim = c(10.5,85), ylim = c(0,140)) +
   theme(axis.title.y = element_blank(),axis.ticks.y = element_blank(),axis.text.y = element_blank())


# SCRUB
datay = all_data[all_data$CBFTYPE =='SCRUB',]
pnc = datay[datay$Datasets=='PNC',]
nki = datay[datay$Datasets=='NKI',]
age = datay[datay$Datasets=='AGE',]
irr = datay[datay$Datasets=='IRR',]
ftd = datay[datay$Datasets=='FTD',]

#############################################################
scrub_Age_gam <- gam(CBF.GM ~ AGE + sex + FD + s(AGE, k=kk), method="REML", data = datay)

#####################
## Look at results ##
#####################
#summary(cbf_Age_gam)

## Nonlinear age effect
Age_pval <- summary(scrub_Age_gam)$s.table[1,4]
Age_pval

####################################
## Visualize Nonlinear Age Effect ##
####################################
plotdata <- visreg(scrub_Age_gam,'AGE',type = "conditional",scale = "linear", plot = FALSE)
smooths <- data.frame(Variable = plotdata$meta$x, 
                      x=plotdata$fit[[plotdata$meta$x]], 
                      smooth=plotdata$fit$visregFit, 
                      lower=plotdata$fit$visregLwr, 
                      upper=plotdata$fit$visregUpr)
predicts <- data.frame(Variable = "dim1", 
                       x=plotdata$res$AGE,
                       y=plotdata$res$visregRes)

scrub_Age_plot <- ggplot() + xlim(8, 85)+ ylim(0,140) +
  #theme(legend.position = "none")  +
  labs(x = "Age (years)", y = "CBF(mL/100 g/min)") +
  theme(axis.title.x = element_text(size = rel(1.6))) +
  theme(axis.title.y = element_text(size = rel(1.6))) + 
  theme(axis.text = element_text(size = rel(1.4))) + theme(axis.line = element_line(colour = 'black', size = .5), axis.ticks.length = unit(.25, "cm")) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank()) +
  geom_point(data = predicts, aes(x, y), colour = "darksalmon", alpha=0.7 ) +  
  #geom_point(data=datay,aes(x=AGE, y=CBF.GM),size=1)+ 
  geom_point(data=pnc,aes(x=AGE, y=CBF.GM),shape=21,size=2,fill='#e34a33', color="white")+ 
  geom_point(data=nki,aes(x=AGE, y=CBF.GM),shape=21,size=2,fill="#3182bd", color="white")+ 
  geom_point(data=irr,aes(x=AGE, y=CBF.GM),shape=21,size=2,fill="#31a354", color="white")+ 
  #geom_point(data=ftd,aes(x=AGE, y=CBF.GM),shape=21,size=2,fill="#d95f02", color="white")+ 
  geom_point(data=age,aes(x=AGE, y=CBF.GM),shape=21,size=2,fill="#c51b8a", color="white")+ 
  geom_line(data = smooths, aes(x = x, y = smooth), colour = "midnightblue",size=1) +
  geom_line(data = smooths, aes(x = x, y=lower), linetype="dashed", colour = "midnightblue", alpha = 0.9, size = 0.9) + 
  geom_line(data = smooths, aes(x = x, y=upper), linetype="dashed",colour = "midnightblue", alpha = 0.9, size = 0.9) +
  coord_cartesian(xlim = c(10.5,85), ylim = c(0,140)) +
theme(axis.title.y = element_blank(),axis.ticks.y = element_blank(),axis.text.y = element_blank())

figure <- ggarrange(basil_Age_plot,pvc_Age_plot,scrub_Age_plot,
                    ncol = 3, nrow = 1,widths=c(2.3,2,2) )
ggsave("ExtendedDataFigure7/ExtendedDataFigure7.pdf", width=10, units="in", height=4,dpi=800)
figure
```